---
title: "API Lab & Homework"
author: "Alex Vand"
date: "10/25/2021"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, message=FALSE}
library(tidyverse)
library(dataRetrieval)
library(metajam)
```

### Exercise 1: Data retrieval

```{r}
siteNumber <- "11118500"
parameterCd <- "00060"  # Discharge
startDate <- "2019-10-01"  
endDate <- "2020-10-05"

data <- readNWISdv(siteNumber, parameterCd, startDate, endDate)
```

```{r}
discharge_plot <- ggplot(data = data, aes(x = Date, y = X_00060_00003)) +
  geom_point() +
  labs(title = "Discharge time series for the Ventura River",
       x = "Date",
       y = "Discharge")
discharge_plot
```

### Bonus

```{r}
siteNumber <- "11118500"
parameterCd <- "00060"  # Discharge
startDate <- ""  
endDate <- "2020-10-05"

all_data <- readNWISdv(siteNumber, parameterCd, startDate, endDate)
min_date <- min(all_data$Date)
```
This stream gauge record started using the API on `r min_date`.

### Assignment 2.1

```{r}
siteNumber <- c(11118500, 11113500)
parameterCd <- "00060"  # Discharge
startDate <- "2021-10-04"  
endDate <- "2021-10-05"

data2 <- readNWISuv(siteNumber, parameterCd, startDate, endDate)
```

```{r}
discharge_plot2 <- ggplot(data = data2, aes(x = dateTime, y = X_00060_00000)) +
  geom_line(aes(color = site_no)) +
  labs(title = "Discharge time series for the Ventura River",
       x = "Date",
       y = "Discharge") +
  scale_color_discrete(name = "Site",
                    breaks = c(11118500, 11113500),
                    labels = c("Ventura", "Santa Paula"))
discharge_plot2
```

```{r}
ventura_data <- data2 %>%
  filter(site_no == 11118500)

ventura_peak <- ventura_data %>%
  filter(X_00060_00000 == max(X_00060_00000))
```

The stream flow at the Ventura location peaked between `r min(ventura_peak$dateTime)` and `r max(ventura_peak$dateTime)`.

```{r}
santa_paula_data <- data2 %>%
  filter(site_no == 11113500)

santa_paula_peak <- santa_paula_data %>%
  filter(X_00060_00000 == max(X_00060_00000))
```

The stream flow at the Santa Paula location peaked between `r min(santa_paula_peak$dateTime)` and `r max(santa_paula_peak$dateTime)`.

### Practice with rain event on 2021-10-25

```{r}
siteNumber <- c(11118500, 11113500)
parameterCd <- "00060"  # Discharge
startDate <- "2021-10-24"  
endDate <- "2021-10-25"

data3 <- readNWISuv(siteNumber, parameterCd, startDate, endDate)
```

```{r}
discharge_plot3 <- ggplot(data = data3, aes(x = dateTime, y = X_00060_00000)) +
  geom_line(aes(color = site_no)) +
  labs(title = "Discharge time series for the Ventura River",
       x = "Date",
       y = "Discharge") +
  scale_color_discrete(name = "Site",
                    breaks = c(11118500, 11113500),
                    labels = c("Ventura", "Santa Paula"))
discharge_plot3
```

```{r}
ventura_data <- data3 %>%
  filter(site_no == 11118500)

ventura_peak <- ventura_data %>%
  filter(X_00060_00000 == max(X_00060_00000))
```

The stream flow at the Ventura location peaked between `r min(ventura_peak$dateTime)` and `r max(ventura_peak$dateTime)`.


```{r}
santa_paula_data <- data3 %>%
  filter(site_no == 11113500)

santa_paula_peak <- santa_paula_data %>%
  filter(X_00060_00000 == max(X_00060_00000))
```

The stream flow at the Santa Paula location peaked between `r min(santa_paula_peak$dateTime)` and `r max(santa_paula_peak$dateTime)`.

### Exercise 2: `metajam`

### Assignment 2.2

Download the data

```{r, eval = FALSE}
data_url <- "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3A7fc6f6db-c5ea-426a-a743-1f2edafb43b8"

local_path <- metajam::download_d1_data(data_url, "C:/Users/Alex Vand/Documents/EDS_213/eds213_week2/download_data")
```

Read the data

```{r}
hh_list <- metajam::read_d1_files(local_path)
hh_data <- hh_list$data
hh_att_metadata <- hh_list$attrubute_metadata
```

Create a plot by year from 2009 to 2015 showing the average percentage of household speaking only English at the State level (one data point per year)

```{r}
english_data <- hh_data %>% filter(Year == c(2009:2015)) %>% 
  group_by(Year) %>% 
  summarize(pct_english = mean(speak_only_english)/mean(total) * 100)
english_data
```


```{r}
english_plot <-
  ggplot(data = english_data, aes(x = Year, y = pct_english)) +
    geom_point() +
    geom_line() +
    labs(y = "Average % of households speaking English only")
english_plot
```








